\documentclass[a4paper]{article}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\author{Jatin Kumar}
\setcounter{secnumdepth}{0}

\titleformat{\section}
{\scshape\large}
{}
{}
{}

\titleformat{\subsection}
{\bfseries\normalsize}
{}
{}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{}
{}

\titlespacing{\section}{0pt}{13pt plus 1pt minus 1pt}{3pt plus 1pt minus 1pt}
\titlespacing{\subsection}{0pt}{5pt plus 1pt minus 1pt}{0pt plus 1pt minus 1pt}

\setitemize{itemsep=-4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
	\makeatletter
	\centering {\huge \@author}
	\makeatother
	\vspace{6pt}

	\href{mailto:jatin208015\@gmail.com}{{\faAt} jatin208015\@gmail.com} |
	{\faPhone } +91-8887982410 |
	\href{https://github.com/jatinkumar-me}{{\faGithub} jatinkumar-me} |
	\href{https://www.linkedin.com/in/jatinkumar-2000-me/}{{\faLinkedin} {jatinkumar2000-me}} |
	{\faMapMarker} Kanpur, India
\end{center}

\vspace{-13pt}
\hrulefill
\vspace{-8pt}

\begin{center}
	Driven \textit{Mechanical Engineering Graduate}. Ready to elevate career in a company to solve real world problems — Adaptable and Driven to Learn, Grow, and Contribute.
\end{center}

\section{Education}
\subsection{Dr. BR Ambedkar National Institute of Technology Jalandhar}
\textit{Bachelor of Technology, Mechanical Engineering}
\hfill
\textit{July 2018 --- June 2022}

Cumulative Grade Point Average --- 7.09

\subsection{Kendriya Vidyalaya No. 2, AFS Chakeri, Kanpur}
\textit{Central Board of Secondary Education}
\hfill
\textit{2016 --- 2017}

Grade --- 83.80\%


\section{Skills}
\subsubsection*{Programming Languages}
JavaScript, TypeScript, Go, MATLAB, Engineering Equation Solver (EES)
\vspace{-10pt}
\subsubsection*{Markup Languages}
HTML5, CSS3, Markdown, \LaTeX
\vspace{-10pt}
\subsubsection*{Tools}
SolidWorks, AutoCAD, EES, Adobe Photoshop, GIMP, Git/GitHub, VS-Code, Eclipse, Postman, GNU/Linux
\vspace{-10pt}
\subsubsection*{Databases}
MySQL, MongoDB

\section{Positions Of Responsibility}
\subsection{Society Of Mechanical Engineers (SOME), NIT-J }
\textbf{Student Head}
\hfill
\textit{January 2021 --- March 2022}
\begin{itemize}
	\item Collaborated with team of 30+ members to organize various edutainment events like Robowars, Manoeuvre, UAE Drone, Rocket League during annual technical fest of college, “Techniti”.
	\item Worked as an Editor/Designer for bi-annual magazine, “Mechazine”. Supervised content selection and editing process, designed graphics and layouts for 8th, 9th and 10th edition of magazine.
	\item Organized industrial visit in Rail Coach Factory Kapurthala, Jalandhar
\end{itemize}

\section{Projects}

\subsection{Performance analysis of Kalina Cycle}
\textit{Using MATLAB, EES, SolidWorks}
\begin{itemize}
	\item Analysis and assessment of performance capability of Kalina cycle was conducted in this project by collaborating with a team of 5 members.
	\item The system was tested for various performance parameters and the results were graphically plotted using EES, for drawing conclusions.
\end{itemize}

\subsection{Augmented Power Organic Flash Cycle of Heat Recovery Power Plant}
\textit{Using EES, SolidWorks}
\begin{itemize}
	\item This project was aimed to assess the true technical potential of the Augmented power OFC technology for low temperature heat sources using Heat recovery.
	\item Development of performance characteristics of Power augmentation using organic flash cycle (OFC) from waste heat recovery.
	\item Design of Fluid Flash Tank using SolidWorks.
\end{itemize}

\section{Work Experience}
\subsection{Junior Software Engineer @ Beingtheparent.com}
\textit{A rapidly growing online discovery platform for parents}
\hfill
\textit{September 2023 -- January 2024}
\textbar
\textit{ Bangalore (Onsite)}
\begin{itemize}
	\item Developed and maintained backend services using Node.js, TypeScript, and Express, ensuring high performance and scalability.
	\item Implemented notification services for various features of the app. Optimized database queries to boost app performance.
	\item Implemented user tracking and analytics API, leveraging data-driven insights to enhance decision-making processes and integrated real-time chat features using Sockets, enhancing user experience.
\end{itemize}

\section{Areas of Interest}
\begin{itemize}
	\item Thermodynamics
	\item IC Engines
	\item Fluid dynamics
	\item Computer Graphics
\end{itemize}


% \section{Courses and certification}
% \subsection{The Complete Web Developer in 2021}
% \textit{Udemy, Course Instructor: Andrei Neagoie}
% \hfill
% \textit{November 2021} \textbar \href{https://www.udemy.com/certificate/UC-13ddb4ce-86c8-4396-9cb7-701f5c522fd8/}{  Certificate \faExternalLink}
%
% Built several frontend as well as full stack projects utilizing various web technologies like HTML, CSS, JavaScript, React, Redux, Node.js, Express.js and PostgreSQL.
\end{document}
