\documentclass[a4paper]{article}
\usepackage{fontawesome}
\usepackage{titlesec}
\usepackage[margin=1cm]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\author{Jatin Kumar}
\setcounter{secnumdepth}{0}

\titleformat{\section}
{\scshape\large}
{}
{}
{}

\titleformat{\subsection}
{\bfseries\normalsize}
{}
{}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{}
{}

\titlespacing{\section}{0pt}{13pt plus 1pt minus 1pt}{3pt plus 1pt minus 1pt}
\titlespacing{\subsection}{0pt}{5pt plus 1pt minus 1pt}{0pt plus 1pt minus 1pt}

\setitemize{itemsep=-4pt}

\pagestyle{empty}

\begin{document}

\begin{center}
	\makeatletter
	\centering {\huge \@author}
	\makeatother
	\vspace{6pt}

	\href{mailto:jatin208015\@gmail.com}{{\faAt} jatin208015\@gmail.com} |
	{\faPhone } +91-8887982410 |
	\href{https://github.com/jatinkumar-me}{{\faGithub} jatinkumar-me} |
	\href{https://www.linkedin.com/in/jatinkumar-2000-me/}{{\faLinkedin} {jatinkumar2000-me}} |
	{\faMapMarker} Bangalore, Karnataka
\end{center}

\vspace{-6pt}
\hrulefill
\vspace{3pt}

\begin{center}
Driven \textit{Full Stack Developer}. Ready to Elevate Career in a Fast-Paced, Product Based (preferrably User-Facing) company — Adaptable and Driven to Learn, Grow, and Contribute. --- 
\end{center}

\section{Skills}
\subsubsection*{Programming Languages}
JavaScript, TypeScript, Java
\vspace{-10pt}
\subsubsection*{Markup Languages}
HTML5, CSS3, Markdown, \LaTeX
\vspace{-10pt}
\subsubsection*{Frameworks and Libraries}
React.js, Express.js, Node.js, Redux Toolkit, RTK Query, React-router-dom, Material-UI, Chakra-UI, Mantine, Styled-Components, Socket.io
\vspace{-10pt}
\subsubsection*{Databases}
MySQL, MongoDB
\vspace{-10pt}
\subsubsection*{Tools}
Git/GitHub, VS-Code, Eclipse, Postman, GNU/Linux

\section{Work Experience}
\subsection{Junior Software Engineer @ Beingtheparent.com}
\textit{A rapidly growing online discovery platform for parents}
\hfill
\textit{September 2023 -- January 2024}
\textbar
\textit{ Bangalore (Onsite)}

\vspace{3pt}
\textbf{Technologies used:}
JavaScript, TypeScript, Node.js, React.js, SQL, MongoDB
\begin{itemize}
	\item Developed and maintained backend services using Node.js, TypeScript, and Express, ensuring high performance and scalability.
	\item Implemented notification services for various features of the app. Optimized database queries to boost app performance.
	\item Implemented user tracking and analytics API, leveraging data-driven insights to enhance decision-making processes and improve overall system performance.
	\item Implemented real-time chat features using Sockets, enhancing user experience.
\end{itemize}
	\textbf{References:} 

	Ranjith Kadamboor, \textit{Vice President, Engineering, Beingtheparent} | ranjith@beingtheparent.com, +91-9591994646

\section{Personal Projects}
\subsection{Discourse: an online discussion platform}
\textit{React, Redux-Toolkit, RTK-Query, Chakra-UI, Node.js, Express.js, MongoDB}
\hfill
\href{https://discourse-app.netlify.app/}{ \faLink }
\textbar
\href{https://github.com/jatinkumar-me/Discourse}{ \faCode}
\begin{itemize}
	\item Built fully responsive user interface with dark mode toggle with Chakra-UI along with an inbuilt rich text editor for adding styled text.
	\item Implemented functionalities like, upvote, downvote, comment and reply with optimistic updates for instant user feedback along with user authentication and authorization using B-crypt and JWT and form validation using Formik and Yup.
\end{itemize}

% \subsection{Social-Book: full-stack social media app}
% \textit{React, Redux-Toolkit, Material-UI, Node.js, Express.js, MongoDB}
% \hfill
% \href{https://discourse-app.netlify.app/}{ \faLink }
% \textbar
% \href{https://github.com/jatinkumar-me/social-book}{ \faCode}
% \begin{itemize}
%     \item Implemented User authentication and authorization using B-Crypt and JSON Web Token. 
%     \item Added features like comment, like, post, add/remove friend. Additionally, added caching of the state and JWT token on local storage using Redux-persist.
% \end{itemize}

\subsection{Type-learn}
\textit{React, Redux-Toolkit, TypeScript}
\hfill
\href{https://type-learn.netlify.app/}{ \faLink }
\textbar
\href{https://github.com/jatinkumar-me/type-learn}{ \faCode}
\begin{itemize}
	\item Built an intuitive user interface along with a virtual keyboard to highlights key presses.
	\item Implemented real time feedback on typing accuracy and incorrectly typed text.
\end{itemize}

% \subsection{Exploding-kittens card game}
% \textit{React, Redux-Toolkit, TypeScript, Node.js, Redis-OM, Express.js}
% \hfill
% \href{https://exploding-kittens.netlify.app/}{ \faLink }
% \textbar
% \href{https://github.com/jatinkumar-me/exploding-kittens}{ \faCode}
% \begin{itemize}
%     \item Exploding kittens is a simple web-based card game where user has to draw a card out of 5 randomly placed cards. 
%     \item Implemented a leader-board system that shows real time score updates of different players currently playing.
% \end{itemize}


\section{Education}
\subsection{Dr. BR Ambedkar National Institute of Technology Jalandhar}
\textit{Bachelor of Technology, Mechanical Engineering}
\hfill
\textit{July 2018 --- June 2022}

Cumulative Grade Point Average --- 7.09

\subsection{Kendriya Vidyalaya No. 2, AFS Chakeri, Kanpur}
\textit{Central Board of Secondary Education}
\hfill
\textit{2016 --- 2017}

Grade --- 83.80\%

\section{Courses and certification}
\subsection{The Complete Web Developer in 2021}
\textit{Udemy, Course Instructor: Andrei Neagoie}
\hfill
\textit{November 2021} \textbar \href{https://www.udemy.com/certificate/UC-13ddb4ce-86c8-4396-9cb7-701f5c522fd8/}{  Certificate \faExternalLink}

Built several frontend as well as full stack projects utilizing various web technologies like HTML, CSS, JavaScript, React, Redux, Node.js, Express.js and PostgreSQL.


\section{Positions of responsibility}
\subsection{Student Head}
\textit{Society of Mechanical Engineers, NIT-Jalandhar}
\hfill
\textit{2021 --- 2022}

Lead a team of 30+ members to organize various technical events for college's annual technical fest and worked as an Editor/Designer for bi-annual magazine, `Mechazine'.


\end{document}

